\section{Introduction}\label{sec:introduction}

% \subsection{The importance of Cahn-Hilliard}%
% \label{sub:the_importance_of_cahn_hilliard}


The first application of the Cahn-Hilliard equation (CH) appeared when modelling phase separation of two-component incompressible fluids \cite{cahn1958free, cahn1959free, cahn1961spinodal}, but was quickly generalized to handle multi-component system
as well \cite{bosch2015fractional, eyre1993systems, toth2016phase, miranville2017cahn}. In engineering, CH is the key component in
the phase-field model, which is a mathematical framework to model transitions and interface dynamics in materials and fluid dynamics \cite{steinbach2009phase, chen2002phase}.
From this has the equation found many interesting applications for a big variety of problems. To mention a few, we have
multiphase fluid dynamical problems \cite{badalassi2003computation, li2016lattice, kim2012phase, shen2010phase}, solidification of binary or multicomponent alloys \cite{kim1999phase, echebarria2004quantitative}, and continuum modelling of fracture dynamics in
materials \cite{kuhn2010continuum, li2015phase}. Perhaps an unexpected application is that CH can be used to for in painting when recovering damaged parts of an image \cite{bertozzi2006inpainting, burger2009cahn, bosch2015fractional, brkic2020image}
and modelling the origin of the irregular structure in the Saturn's rings \cite{tremaine2003origin}.
CH has also shown be be essential in many areas of biology and medicine. From a macroscopic point of view is that CH is a great tool to model tumor growth, wound healing and brain tumors \cite{agosti2017cahn, cristini2009nonlinear}.
On the microscopic level on the bio membrane is there a ongoing hypothesis about the existence of the accumulation of lipids into so-called lipid rafts which serve as a rigid platform for proteins with
special properties such as signalling and intercellular trafficking \cite{ levental2020lipid, hancock2006lipid, munro2003lipid, simons1997functional}. It turns out that the hypothesis can tested by modelling the problem as a separation problem using
CH \cite{miller2020divide, garcke2016coupled, yushutin2019computational}.

\subsection{The Cahn Hilliard Equation}%
\label{sub:the_equations}

% \todo[inline]{ Derivation of the Cahn-Hilliard equation from its energy functional. }
The Cahn-Hilliard equation comes in many variants depending on its application, but we will in this report on the binary mixture version \cite{miranville2017cahn}. Let $\Omega \subset  \mathbb{R} ^{d} $ be a compact set for $d=2,3$ with boundary
$\Gamma $. We define the time duration parameter $T \in  [0,\infty) $ and the
so-called unknown phase-field function as the
mapping $u: \left[ 0,T \right] \times \Omega  \to \left[ -1,1 \right]  $, which is denoted as the local difference of a binary mixture of two concentrations $c_{A}, c_{B} \in \left[ 0,1\right] $ s.t. $u = c_{A} -c_{B}$ and $c_{A} + c_{B} = 1$. Remark that if there exist a
local point so $u$ has the extreme value $-1$, then it implies that the particular point has $100\%$ concentration $c_{A}$ and vice-versa for $c_{B}$. On the other hand, if $u$ is zero it implies that the mixture is $50\% - 50\%$.

For a isotropic
binary mixture nonuniform, the standard Ginzburg-Landay free energy functional is given by \[
E( u)  = \int_{\Omega }^{} \frac{\varepsilon ^2}{2} \abs{ \nabla u } ^2 + F( u) dx
\]
The nonlinear function $F( u) $ is denoted as the (Helmholtz) free energy density associated with the interaction dynamics between the components and thus comes in many forms depending on the thermodynamic properties, see \cite{miranville2017cahn}.
However, we will in this article assume that $F( u) = ( 1 / 4 ) ( 1- u^2) ^{4} $.
We choose to define the chemical potential $\mu $ as the variational derivative,
\[
\mu = \frac{ \delta E( u) }{ \delta  u} = f( u)  - \varepsilon ^{2} \Delta c .
\]
where we used the notation $f( u) = F'( u) $.
First of all, to require local mass conservation we may enforce the continuity equation, that is \[
\partial _{t} u + \nabla \cdot \mathcal{J}  = 0,
\]
where $J$ denotes the flux governed by the physical dynamics. Hence, this naturally leads the no-flux and the Neumann boundary conditions,
\begin{equation}
\label{eq:conservation}
    \begin{split}
\mathcal{J}  \cdot n & = 0 \text{ on } \Gamma \\
\partial _{n} u & = 0 \text{ on } \Gamma
    \end{split}
\end{equation}
 A well accepted law for the flux  is to proportional to the gradient of the chemical energy, $\mathcal{J} = - M  \nabla \mu  $ for a parameter $M$.
Thus, we finally have the strong form Cahn-Hilliard equation. Let $ u( x,0) =  u_{0}$ then is the dynamics on the form,

\begin{equation}
\label{eq:strongch}
    \begin{split}
\partial _{t} u  = \Delta ( f( u)  - \varepsilon ^2 \Delta u ) &\quad \text{ in } \Omega  \\
\partial _{n} u = 0 \quad &\text{ on } \Gamma  \\
\partial _{n}(f( u)  - \varepsilon ^2 \Delta u )  = 0 \quad &\text{ on } \Gamma  \\
    \end{split}
\end{equation}

Based on these laws and the boundary conditions, it becomes evident that the energy functional serves as a Lyapunov function in the sense that its time derivative is monotonically decreasing and that the global mass concentration is zero, i.e.
\[
    \begin{split}
\frac{d}{dt} E( u)  \le  0 \text{ and }\frac{d}{dt} \int_{\Omega }^{}  u dx = 0.
    \end{split}
\]
Remark that the computation of the inequality does utilize the assumption of $M$ to be constant and both equations require the no-flux boundary condition, $\mathcal{J} \cdot n = 0$.
For details, see \cite[Equation 17 ]{lee2014physical} and \cite[Equation 1.7]{garcke2020weak}.
This is useful since we expect $E( u( \cdot , t_{2}) ) \le  E( u( \cdot , t_{1}) ) $ for $0 < t_{1} < t_{2} $ and that the global mass is conserved, \[
\int_{\Omega }^{} u ( x,t)  dx = \int_{\Omega }^{} u_{0}(x)  dx.
\]
The properties under consideration serve as a theoretical foundation for establishing the existence, uniqueness, and long-term behavior of the problem. Consequently, these properties are well-comprehended from a mathematical standpoint. For
references, see \cite{abels2007convergence, cherfils2011cahn,
elliott1986cahn}.

\subsection{Numerical Methods}%
\label{sub:numerical_methods}

\todo[inline]{ Describe the most common ways to solve this problem. FVM? FDM? FEM? One paragraph}
\todo[inline]{ Describe why we ended up with a finite element. What methods are used in FEM? Methods to handle the non-linearities? Methods for time discretization? Methods to handle smooth geometries? Methods to handle moving domains?}

CIP formulation of the Cahn-Hilliard was presented in \cite{wells2006discontinuous} which avoids high derivatives along boundaries, thus no need for global $C^{1}$ elements.

Alternatives to smooth boundaries is isogeometric analysis, which is based on NURBS, and does in fact handle complex geometries quite well \cite{hughes2005isogeometric}.

Mixed CutFEM formulation of Cahn-Hilliard \cite{karatzas2021reduced} and a mixed Hybrid High-Order method \cite{chave2016hybrid}. Isogeometric formulation of Cahn-Hilliard \cite{kastner2016isogeometric, gomez2008isogeometric} and unfitted versions \cite{zhao2017variational}. Isogeoemtric formulation on moving
surfaces \cite{zimmermann2019isogeometric}. Virtual $C^{1}$  elements has also been considered \cite{antonietti2016c}.

Introduced unconditionally stable, second order accurate, numerically dissipative with parameters $\alpha$ and $ \beta $,  Newmans Method \cite{newmark1959method}
Improved versions of the Newmark method by introducing the numerically dissipative parameters such as the Hilber method and the Bossak Method \cite{hilber1977improved, wood1980alpha}. Combing these ideas the Generalized $\alpha $ method from which all the other methods can be derived \cite{chung1993time}.

% \subsection{CutFEM}%
% \label{sub:cutfem}
% The goal of this thesis is to make a foundation of a numerical framework, which later can be developed to handle moving domains. We will use CutFEM method \cite{burman2015cutfem}.


% \subsection{ODE integrators}%
% \label{sub:ode_integrators}

% First signs of finite element was in 1941 when Hrennikoff used the method solve problems in linear elasticity \cite{hrennikoff1941solution}. It then took offspring to applications in aerospace application in the 50's when it was formalized the method
% could solve dynamical problems on complex structures as a competitor to the finite difference method
% \cite{argyris1960energy, turner1956stiffness, liu2022eighty}. To expect good numerical results does he finite element methods requires a lot of DOFs and thus did the popularity climb with the rise of the supercomputers. Thus it has proven to be
% useful found a great variety of applications in multi-physics problems because of its simplicity based on the abstract mathematical generalisation of both functions spaces and computational domains.

\subsection{Outline of the report}%
\label{sub:outline_of_the_report}
\todo[inline]{ Describe the workflow of this method. }


The goal of the thesis implement an modern unfitted finite element method (FEM) to solve the Cahn-Hilliard equation. The plan is to first derive the stability and well-posedness for the method for the fourth order Biharmonic equation,
\[
    \begin{split}
\Delta ^2 u & = f \quad  \text{in } \Omega \\
\partial _{n} u & = g_{1} \quad \text{ on } \Gamma  \\
\partial _{n} \Delta u  & = g_{2} \quad \text{ on } \Gamma
    \end{split}
\]
\begin{enumerate}[label=(\alph*)]
    \item Derive an unfitted cut continuous interior penalty method (CutCIP) for the biharmonic equation and show that the method is well-posed.
    \item Implement a time discretization scheme of an linear Cahn-Hilliard equation.
    \item Implement nonlinear iteration methods for the (nonlinear) Cahn-Hilliard Equation.
\end{enumerate}
