
\section{Mathematical Background}%
\label{sec:mathematical_background}

In this section, we revisit the established definitions and provide a brief overview of Sobolev spaces. Afterward, we briefly review the finite element method and discuss the necessary tools required for calculating a priori estimates. We will
generally follow the formulations presented in \cite{pietro2012, ErnGuermond2021}.


\subsection{Sobolev spaces}%
\label{sub:notation}

We will in this report assume $\Omega $ to be a compact and open set in $\mathbb{R} ^{d}$. Let $p \in \mathbb{R} $, $ 1 \le  p \le  \infty$, and  define the space $L^{p}\left( \Omega  \right) $ to be the set of all measurable functions $u: \Omega  \mapsto \mathbb{R} $ such that
$\left\lvert f \right\rvert ^{p}$ is Lebesgue integrable, i.e,

\begin{equation*}
    L^{p}\left( \Omega  \right) = \left\{ u: \Omega \mapsto \mathbb{R}  \mid \int_{\Omega }^{} \left\lvert u \right\rvert ^{p} d \Omega  < \infty  \right\}
.\end{equation*}
Let $u \in L^{p}\left( \Omega  \right) $. We define the integral norm of order $p$ to be \[
\| u \|_{ L^{p}\left( \Omega  \right)  }^{  }  = \left( \int_{\Omega }^{} \left\lvert u \right\rvert ^{p} dx  \right) ^{\frac{1}{p}}.
\]

The following definition for derivatives is employed.
For $d$ dimensions of order $k$ we define the multi-index $\alpha  = ( \alpha _{1}, \ldots, \alpha _{d})  $ with the absolute value $\abs{ \alpha  } = \sum_{i=1}^{d}  \alpha _{i} = k $ such that
\begin{equation}
    \label{eq:der}
\partial ^{\alpha} u = \frac{\partial ^{ \alpha_{1}  }  } {\partial^{} x_{1}^{\alpha _{1}}  } \ldots \frac{\partial ^{ \alpha_{d}  }  } {\partial^{} x_{d}^{\alpha _{d}}  } u \quad  \text{for }u \in C^{\left\lvert \alpha  \right\rvert }( \Omega )
\end{equation}

  Let $k\ge 0$ be an integer and let $1 \le  p <  \infty$ be a real number, then the Sobolev space $W^{k,p}( \Omega ) $ is defined by
  \begin{equation}
W^{k,p}\left( \Omega  \right) = \left\{ u \in L^{p}\left( \Omega  \right)  \mid  \partial ^{\alpha } u \in L^{p}\left( \Omega  \right)  \forall \alpha : \left\lvert \alpha  \right\rvert  \le k \right\}.
  \end{equation}
with the corresponding norm
\begin{equation}
\| u \|_{ W^{k,p}\left( \Omega  \right)  }^{  }  = \left(   \sum_{j = 0}^{k}  \left\lvert u \right\rvert ^{p} _{  W^{j,p}\left( \Omega  \right) } \right)^{\frac{1}{p}} .
\end{equation}
Here the seminorm is defined such that $ \left\lvert u \right\rvert _{W^{k,p}( \Omega  ) }^{} =  ( \sum_{\left\lvert \alpha  \right\rvert  = k}^{} \| \partial ^{\alpha }u \|_{ L^{p}( \Omega )   }^{ p } )^{\frac{1}{p}} $.

For shorthand notation, we denote
\begin{equation}
    \begin{split}
\| \cdot \|_{k,p}^{  } & = \| \cdot  \|_{k,p,\Omega   }^{  } = \| \cdot  \|_{ W^{k,p}( \Omega )   }^{  }, \\
   \abs{ \  \cdot \ }_{k,p}^{  } &= \abs{ \   \cdot \ }_{k,p,\Omega   }^{  } = \abs{ \  \cdot \ }_{ W^{k,p}( \Omega )   }^{  },
    \end{split}
\end{equation}

Since $p=2$ is frequently used in this report, we also define for convenience a compact notation $\| u \|_{ \Omega  }^{  }  = \| u \|_{ L^{2}\left( \Omega  \right)  }^{  } $ and $H^{m}( \Omega ) = W^{m,2}( \Omega )  $ such that,
\begin{equation}
\begin{split}
\| \cdot  \|_{H^{m}( \Omega )   }^{  } & = \|   \cdot  \|_{k,\Omega   }^{  } = \|   \cdot  \|_{k,2,\Omega   }^{  },  \\
\abs{ \   \cdot \  }_{H^{m}( \Omega )   }^{  } & = \abs{ \   \cdot \  } _{k,\Omega   }^{  } =  \abs{ \ \cdot \   } _{k,2,\Omega   }^{  }.
\end{split}
\end{equation}

Recall that $L^{2}( \Omega ) $ and $H^{m}( \Omega ) $ are Hilbert spaces equipped with the inner products
\begin{equation}
    \begin{split}
\left( u,v \right) _{\Omega } & = \left( u,v \right) _{L^2\left( \Omega  \right) } = \int_{\Omega }^{} u  v dx, \quad \forall u,v \in L^{2}( \Omega )  \\
    \left( u,v \right) _{m,\Omega } & = \sum_{\left\lvert \alpha  \right\rvert  \le  m}^{}  ( \partial ^{\alpha } u ,  \partial ^{\alpha } v )_{\Omega }, \quad  \forall u,v \in H^{m}( \Omega  ).
    \end{split}
\end{equation}

 let $u,v \in H^{2}(\Omega)$ be scalar functions. The following are the definition for their corresponding operator inner products.

\begin{equation}
\begin{split}
( \nabla v, \nabla u)_{\Omega } & = \int_{\Omega } \nabla v \cdot \nabla u \ dx \\
( \Delta v, \Delta u)_{\Omega } & = \int_{\Omega } \Delta v \Delta u \ dx \\
( D^2 v, D^2 u)_{\Omega } & = \int_{\Omega } D^2 v : D^2 u \ dx \\
\end{split}
\end{equation}
Also, $ \|  \nabla v\|_{  \Omega}^{2} = ( \nabla v, \nabla v)_{\Omega}$, $ \|   \Delta v \|_{\Omega}^{2} = (\Delta v, \Delta v)_{\Omega}$, and $ \| D^2 v \|_{ \Omega}^{2} = (D^2 v, D^2 v)_{\Omega}$.
Here, $\nabla v \cdot \nabla u$ and $D^2 v : D^2 u$ represent the inner product of the gradients and the Frobenius inner product \footnote{
The Frobenius inner product for for two tensors $A, B \in \mathbb{R} ^{\overbrace{n \times n \times \ldots \times n}^{r \text{ times }} } $ is defined such that $ A:B = \sum_{1\le  i_{1}, \ldots, i_{r} \le  d}^{} A_{i_{1} \ldots i_{r}} B_{i_{1}
    \ldots
i_{r}}  $.
} of Hessian matrices, respectively.

Let $v \in H^{r}( \Omega ) $, we define $D^r v$ to be a tensor of order $r$ such that
\begin{equation}
    \label{eq:tensor}
\left[ D^r v \right] _{i_{1} \ldots i_{r}} = \frac{\partial^r v}{\partial x_{ i_{1} } \ldots \partial x_{ i_{r} } } \quad  \forall i_{1}, \ldots, i_{r} \in \left\{ 1,\ldots,d \right\}
\end{equation}
where the norm $\| D^r v\|_{\Omega   }^{ 2 } =
\int_{\Omega }^{} D^r v : D^r v \ dx$ is defined via the standard Frobenius inner product. Observe that this notations holds such that $D^{0} v = v$, $ D^{1} v = \nabla v $ and $D ^{2} v  = J(\nabla v) = \mathrm{Hess}(v)$, where $J$ is the Jacobian operator .

Given the context of Sobolev spaces, we consider the functions $ u \in H^{2}( \Omega )$ and $ v \in H^{1}( \Omega )$. We can denote Greens theorem, which links integrals over a volume and its boundary, as follows,
\[
( \Delta u, v) _{\Omega } = -( \nabla u, \nabla v)_{\Omega } + ( u, \partial _{n}v)_{\Gamma }
\]
This identity serves as an essential tool for the calculations done.



\subsection{Computational Domains}%
\label{sub:computational_domain}
Assume that $\Omega \subset \mathbb{R} ^{d} $ is an open and bounded domain with a boundary $\Gamma $. In standard FEM methods a key assumption is that the set $\Omega $ is a polyhedra. This is useful since a polyhedra can be fully covered by a collection of polyhedra and, hence, motivating us to define a fitted mesh.
We define a fitted mesh $\mathcal{T} $ of the domain $\Omega $ to be a collection of closed polyhedra $\left\{ T \right\}  $ with disjoint interior forming a partition of $\Omega $ such that $\overline{\Omega } = \bigcup _{T \in \mathcal{T} } T $, for illustration see Figure
\ref{fig:domain_mesh}.
Here we say that each $T \in  \mathcal{T} $ is a mesh element or an element.
The mesh size is defined as the maximum diameter $h := h_{max} $ of any polyhedra in the mesh $\mathcal{T} = \left\{ T \right\}  $, that is, $ h_{max} = \max_{T \in \mathcal{T} }  h_{T}$ s.t.
$h _{T}  = \mathrm{diam}\left( T \right)   = \mathrm{max}_{x_1, x_{2} \in T} \ \mathrm{ dist }(x_{1}, x_{2})$
Hence, motivating us to use the notation $\mathcal{T} _{h}$ for a mesh $\mathcal{T} $ with size $h$.

For simplicity we restrict ourself to simplicial and quadrilateral elements.
A mesh $\mathcal{T}_{h}$ in $ \mathbb{R} ^{d}$ is said to be matching if
for all neighbouring elements $T_{1}, T_{2} \in \mathcal{T} _{h}$ such that the intersection is non-empty, $T_{1} \cap T_{2} \neq \emptyset  $, then $T_{1}\cap T_{2}$ is for $d=2$ either a common vertex, edge, and for $d=3$ a common vertex, edge or a face.

Let the chunkiness parameter $c_{T} := h_{T}/r_{T}$, where $r_{T}$  is the largest ball that be inscribed inside a element $T \in \mathcal{T}_{h} $.
A mesh is said to be shape regular if $c_{T}\le  c$ is independent of $T$  and $h$. We also say that the mesh is quasi-uniform only if it is shape regular and $h_{\mathrm{ max }} \le  c h_{\mathrm{ min }}$.
For a more complete description of meshes, see \cite[Chapter 8]{ErnGuermond2021}.

In this thesis will we assume that a mesh $\mathcal{T}_{h} $ is matching, shape regular and quasi-uniform unless specified.
 The fact that the mesh is conform makes is a useful property since the interface between mesh elements has come into contact in the sense
that it is either a vertex or a facet. This with the combination of shape regularity and quasi-uniformity is a major key to prove important inequalities in broken Sobolev spaces \cite[Chapter 1.4.1]{pietro2012}. Hence, the assumptions are very handy when proving convergence.


Let $\mathcal{T}_{h}  = \left\{ T \right\} $ be a mesh of $\Omega \subset  \mathbb{R} ^d $ consisting of polygons $T \in \mathbb{R} ^{d}$.
The set of all facets is the union of external and internal facets, $\mathcal{F} _{h} = \mathcal{F} ^{ext}_{h} \cup \mathcal{F} _{h}^{int} $, where each are defined by
\[
            \mathcal{F}^{int} _{h}  = \left\{ F=T^{+}\cap T^{-}  \mid  T^{+}, T^{-} \in \mathcal{T}_{h}  \right\} \text{ and }
            \mathcal{F}^{ext} _{h}  = \left\{ F= \partial T \cap \partial \Omega    \mid  T  \in \mathcal{T}_{h}  \right\}.
\]
Assume $T^{+} \neq T^{-}$ . Next, we define the following normal vectors.
\begin{enumerate}[label=\arabic*)]
    \item We define $ n= n  _{\partial T}$ to be unit outward normal on $\partial T$ for each $T \in \mathcal{T}_{h} $
\item Let $F \in \mathcal{F }^{int} _{h}$. We define $n$ to be the facet normal $ n =  n _F = n | _{\partial T^{+}} $  from $T^{+}$ to $T^{-}$, illustrated in Figure \ref{fig:normal}.
 \item Let $F \in \mathcal{F} ^{ext}_{h}$. Then we define the facet normal $n | _{F} = n | _{\partial T} $ to be the unit outward normal.
\end{enumerate}
Please note that we for convenience employ the notation $n$ when it is clear what entity the normal is associated with.

    Let $v\in L^2( \Omega ) $ be a scalar function on $\Omega$ with a corresponding shape regular and quasi-uniform mesh $\mathcal{T}_{h} $. We will use the following definitions.
    \begin{enumerate}[label=\arabic*)]
        \item Let $F \in \mathcal{F}^{int} _{h}$ and $v^{\pm}| _{F} = \lim_{t\to 0^{+}} v( x \mp tn)   $ for $x \in F$. We define the mean as $\mean{ v} |_{F} = \frac{1}{2} (v^{+}_{F} + v^{-}_{F})   $ and the jump as $\jump{v}|_{F} =  v^{+}_{F} - v^{-}_{F} $.
        \item Let $F \in \mathcal{F}^{ext} _{h}$ and let $ v( x) =  v(x)|_{F} $ for  $x \in F$.
We define the mean as $\mean{ v} |_{F} = v    $ and the jump as $\jump{v}|_{F} = v$.

    \end{enumerate}
    To simplify will we use the notation $\mean{ v } = \mean{ v }|_{F}    $ and $\jump{ v } = \jump{ v }| _{F}    $ for all $F \in \mathcal{F} _{h}$.
    Remark that if we have two functions $u,v$, for which $u^{\pm}( x) $ and $v^{\pm}( x) $ are defined, then the following identity holds $  \jump{ uv }    = \jump{ u }   \mean{ v }    + \mean{ u }  \jump{ v }$ along all facets $ \mathcal{F}_{h} $ associated with the
    triangulation $\mathcal{T} _{h}$.


\begin{figure}[h!]
\centering
\begin{tikzpicture}[scale=1]
\coordinate (A) at (-1.5, -0);
\coordinate (C) at (0,3);
\coordinate (B) at (4,0);
\coordinate (D) at (4,3.5);

\draw (A) -- (B) -- (C) -- cycle;
\draw (B) -- (C) -- (D) -- cycle;
\fill[red, opacity=0.5] (A) -- (B) -- (C);
\fill[blue, opacity=0.5] (B) -- (C) -- (D);
\draw[ultra  thick] (C) -- (B);

\coordinate (Tm) at (3.6,1.5);
\coordinate (Tp) at (2.0, 0.5);
\coordinate (e) at (0.5, 2.2);
\node[below left] at (Tm) {$T^{-} $ };
\node[above right] at (Tp) {$T^{+}$ };
\node[below right] at (e) {$F$ };

\coordinate (start) at (1.7, 1.7);
\coordinate (endPlus) at (2.25, 2.4);
\coordinate (endMinus) at (1.15, 1.0);

\draw [->, thick] (start) -- (endPlus);
\node[above right] at (endPlus) {$n^{+}$};

\draw [->, thick] (start) -- (endMinus);
\node[below left] at (endMinus) {$n^{-}$};

\end{tikzpicture}

\caption{Facet $F \in \mathcal{F}_h^{int} $ shared by the triangles $T^{+}, T^{-} \in \mathcal{T}_{h} $ and the normal unit vector $n^{+}$ and $n^{-}$. If we pick $T=T^{+}$ and want to evaluate the normal vector $n$ along a facet $F$, then we define $n = n  \mid _{F} = n^{+}$.}
    \label{fig:normal}
\end{figure}



\subsection{Broken Sobolev spaces}%
\label{sub:broken_sobolev_spaces}

In this work will we compute norms on discontinuous elements, thus, it will be necessary to define broken Sobolev spaces.
Let $\mathcal{T}_{h} $ be a mesh and some integer $m\le n$. Then we define the broken Sobolev space to be \[
    \begin{split}
H^{m}( \mathcal{T}_{h} ) & := \left\{ v \in L^2( \Omega )  \mid \ v|_{T} \in H^{m}( T) \quad     \forall T \in  \mathcal{T}_{h} \right\}\\
        L^{2}( \mathcal{F}_{h} ) &:= \left\{ v \in L^2( \mathcal{T}_{h}  )  \mid   \ v|_{F} \in L^{2}( F)  \quad  \forall F \in  \mathcal{F}_{h}   \right\}.
    \end{split}
\]
This motivates us to define broken Sobolev norms and inner products using summation over mesh elements,
\[
 \| v \|_{H^{m}( \mathcal{T}_{h} ) }^{2} = \sum_{T \in  \mathcal{T}_{h} }^{} \| v  \|_{ H^{m}( T ) }^{2  } \quad \text{ and } \quad
 (v ,w )_{ m, \mathcal{T} _{h} }^{} = \sum_{T \in \mathcal{T} _{h}}^{} (v ,w )_{ m,T }^{  } .
\]
As before, we use the shorthand notation,  $\| v \|_{\mathcal{T}_{h}} =  \| v \|_{L^{2}( \mathcal{T}_{h} ) }$ and  $(v ,w )_{ \mathcal{T}_{h} }^{} = (v ,w )_{L^2( \mathcal{T}_{h} ) }^{} $.
That is,
\[
 \| v \|_{L^{2}( \mathcal{F}_{h} ) }^{2} = \sum_{F \in  \mathcal{F}_{h} }^{} \| v  \|_{ L^{2}( F ) }^{2  } \quad \text{ and } \quad
 (v ,w )_{L^{2}( \mathcal{F}_{h} ) }^{} = \sum_{T \in \mathcal{F} _{h}}^{} (v ,w )_{ L^{2}( F ) }^{  } .
\]
Again, we often use the more compact notation $\| v \|_{\mathcal{F}_{h}} =  \| v \|_{L^{2}( \mathcal{F}_{h} ) }$ and  $(v ,w )_{ \mathcal{F}_{h} }^{} = (v ,w )_{L^2( \mathcal{F}_{h} ) }^{} $.
Often  it is needed to integrate over boundaries of elements $\partial \mathcal{T} _{h}  = \left\{ \partial T \  \mid \  \forall T \in \mathcal{T}_{h} \right\}  $, hence, we also denote the notation $\| \cdot  \|_{ \partial \mathcal{T} _{h} }^{  } = \sum_{T \in \mathcal{T} _{h} }^{} \| \cdot  \|_{ \partial T }^{  }
=\sum_{T \in \mathcal{T} _{h} }^{} \sum_{F \in \partial T}^{}  \| \cdot  \|_{ F }^{  }  $.

A very useful lemma when working with estimates on broken Sobolev spaces is that a if a function is continuous, then the jump between the mesh elements is zero. Keep in mind a function $ v \in  H^{1}( \mathcal{T}_{h} ) $ belongs to $ H^{1}( \Omega )  $ if and only
if $ \jump{ v }   = 0 \  \forall F \in \mathcal{F}^{int}_{h}$, see \cite[Lemma 1.23]{pietro2012}.

Recall, the "$\lesssim$" symbol denotes an inequality up to a constant factor. That is, given $a,b >0 $, the statement $a \lesssim b$ is true if there exists a constant $C>0$ such that $a \leq Cb$. Generally, this constant will contain
information related to the properties of the mesh, such as shape regularity and quasi-uniformity, but it often also includes the maximum finite number or measure of a quantity. For instance, let  $w , v_{i} \in L^{2}( \Omega ), \ a_{i} \in \mathbb{R}  \text{ for } i =
1,\ldots,N  $   and  $ \| w \|_{\Omega   }^{  }  =  \| \sum_{i}^{N} a_{i}  v_{i} \|_{\Omega   }^{  } $, then is $ \| w \|_{\Omega   }^{  }
\lesssim \sum_{i}^{N}  \  \| v_{i} \|_{\Omega   }^{  }  $. To maintain clarity and avoid unnecessary complexity, we will not delve into this particular detail related to the constant.

We can express several general useful
basic inequalities and estimates.
\begin{enumerate}[label=(\roman*)]
    \item A fundamental property of the inner-product the so-called Cauchy-Schwarz inequality
        \begin{equation}
            \label{eq:cauchy-schwartz}
     ( u,v)_{m,\Omega   }   \le \| u \|_{m,\Omega    }^{  } \| v \|_{m,\Omega     }^{  }\quad  \forall u,v \in H^{m}( \Omega ).
        \end{equation}

    \item Let $v \in  H^{m}( \Omega ) $, then is
        \begin{equation}
            \| D^{m}v \|_{\Omega   }^{  }  \lesssim \| v \|_{m,\Omega   }^{  }.
        \end{equation}
        Similarly is $\| \Delta  v \|_{\Omega   }^{  } \lesssim \| v \|_{2,\Omega   }^{  }  $.


    \item For all  $u \in L ^{2}( \mathcal{T} _{h})$ we have,
\begin{equation}
    \label{eq:mean_jump_estimate}
    \begin{split}
        \| \jump{  u }   \|_{ \mathcal{F} _{h} }^{  } & \le \|  u^{+}   \|_{ \mathcal{F} _{h} }^{  } +
        \| u^{-}   \|_{ \mathcal{F} _{h} }^{  }  \lesssim  \| u \|_{ \partial\mathcal{T }_{h}  }^{2  },\\
        \| \mean{ u }   \|_{ \mathcal{F} _{h} }^{  } & \le \| u^{+} \|_{ \mathcal{F} _{h}  }^{  } + \| u^{-} \|_{ \mathcal{F} _{h}  }^{  }    \lesssim  \| u \|_{ \partial\mathcal{T }_{h}  }^{2  }.
    \end{split}
\end{equation}

    \item For any $a,b > 0 $ the well known Young's $\varepsilon $-inequality is on the form,
        \begin{equation}
            \label{eq:young-epsilon}
            2ab \le \varepsilon a^2+ \frac{1}{\varepsilon } b^2.
        \end{equation}


\end{enumerate}



% \begin{enumerate}[label=(\roman*)]
%     \item General inverse inequality.
%     Let $\alpha = ( \alpha _{1}, \ldots, \alpha _{N}) $ and $\beta = ( \beta _{1}, \ldots, \beta _{N} ) $.
%     Assume $u \in H^{\abs{ \beta  }  }( T) $. The following inverse inequalities hold.
%     \[
%         \begin{split}
%         \| \partial ^{\alpha } u \|_{T  }^{  } & \lesssim h^{ - \abs{ \beta  }  } \| \partial ^{\alpha - \beta } u \|_{T }^{  } \\
%         \| \partial ^{\alpha }_{n} u  \|_{F  }^{  } &\lesssim h^{-\frac{1}{2}  } \| \partial ^{\alpha } u \|_{T }^{  }
%         \end{split}
%     \]
% \end{enumerate}
    % For a full triangle we have \[
    % \| v \|_{ \partial T }^{  } \lesssim h_{T}^{-\frac{1}{2}} \| v \|_{ T }^{  } + h_{T}^{\frac{1}{2}} \| \nabla v \|_{ T }^{  }
    % \]




\subsection{Lax-Milgram lemma}%
\label{sub:lax_milgram_lemma}

The intention is to introduce a abstract framework which can handle various types of partial differential equations (PDE). Let  $\mathcal{A} : X \to Y $ be a abstract linear operator encoding the structure of any linear PDE, including boundary
conditions and $X,Y$ are spaces of functions. Then we denote the abstract strong formulation as the equation
\begin{equation}
\label{eq:strong_abs}
\mathcal{A} u = f.
\end{equation}
Where the function $f: \Omega \subset \mathbb{R}^d \mapsto \mathbb{R}$. We assume that the function $u: \Omega \rightarrow \mathbb{R}$ satisfies the relation \eqref{eq:strong_abs} pointwise so that $\mathcal{A} u(x)=f(x) \forall x \in \Omega$.
We will discover that Sobolev spaces are specifically engineered to study these kinds of problems.

\begin{definition}[Linear bounded functional]
    \label{def:linear_function}
Let $V$ be a Hilbert space. Furthermore, we define the dual space $V' $ to be the space of linear and bounded functionals $F: V  \mapsto \mathbb{R} $, i.e., \[
V'  = \left\{ F: V \to \mathbb{R}   \mid  F \text{ is linear and bounded} \right\}
\]
\end{definition}

\begin{problem}[Abstract linear problem]
    \label{def:abstract_linear_problem}
    Assume $X$ and $Y$  to be two Hilbert spaces. Let the vector space $\mathcal{L}( X,Y)  $ be all linear bounded operators spanned from $V$ to $Y$. We define the abstract linear problem as follows; find $u \in V$ s.t. \[
    a( u,v)  = l(v ) := \left<f,v \right>_{V' , V}  \forall v \in V
    \]
    Where $a \in  \mathcal{L} ( V, V,\mathbb{R} ) $ is a bounded bilinear form and $f \in V':= \mathcal{L} ( V,\mathbb{R} )  $ is a bounded linear form associated with the abstract strong formulation \eqref{eq:strong_abs}. Here we denote by $\left<\cdot ,\cdot  \right>_{V',V} $ the duality pairing between $V'$ and $V$.

\end{problem}


\begin{definition}[Coercivity and Boundedness]
    \label{def:coercivity}
    Let $V$ be a Hilbert space and let $a( \cdot ,\cdot )  \in  \mathcal{L} ( V, V,\mathbb{R} )  $. Recall that the bilinear form $a( \cdot ,\cdot ) $ is coercive if \[
     a( v,v) \gtrsim  \| v \|_{ V }^{  } \quad  \forall v \in  V.
    \]
     The bilinear form $a( \cdot ,\cdot ) $ is said to bounded if   \[
    a( u,v)  \lesssim  \| u \|_{ V }^{  }  \| v \|_{V }^{  }\quad  \forall u,v \in V.
    \]
\end{definition}


\begin{lemma}[Lax-Milgram]
    \label{def:lax-milgram}
    The abstract linear problem \ref{def:abstract_linear_problem} is well-posed if $a(\cdot , \cdot  ) $ is bounded and coercive. Moreover, the following a priori estimate holds true.\[
    \| v \|_{ V }^{  } \lesssim  \| f \|_{ V'  }^{  }
    \]
\end{lemma}
\begin{proof}
    The problem can easily be proved using a special case of the Banach–Nečas–Babuška theorem. See \cite[Lemma 1.4]{pietro2012}
\end{proof}



\subsection{Finite element method}%
\label{sub:finite_element_method}


The finite element method (FEM) is a numerical method to solve partial differential equation by finding an approximation of the Problem \ref{def:abstract_linear_problem}.  Let $V_{h}$ be a finite-dimensional (polynomial) approximation space on the mesh
$\mathcal{T} _{h}$. We say that a method is conform if $V_{h}\subset V $ and non-conform if $V _{h} \not\subset V$. We define the approximate problem as follows.
\begin{problem}[The approximate problem]
    \label{def:approx_problem}
    Let $V_{h} \not\subset V$ a non-conform finite-dimensional space. Find  $u_{h} \in V_{h}$ such that, \[
    a_{h}(u_{h},v ) = l_{h}( v) :=  \left<f,v \right>   \forall v \in V_{h}.
    \]
\end{problem}

We denote the functional $a_{h}: V_{h} \times V_{h} \to \mathbb{R} $ as an consistent approximation of $a: V \times V \to \mathbb{R} $, and similarly for the right-hand side $l_{h} : \times _{h} \to \mathbb{R} $ as an approximation of $l: V \to \mathbb{R} $.

\begin{definition}[Local polynomial space]
    \label{def:local_space}
    Let $T$ be a element in a mesh $\mathcal{T}_{h} $,  $x = \left[ x_{1}, \ldots, x_{d} \right] $ be a vector, and $\alpha  = \left[ \alpha _{1}, \ldots, \alpha _{d} \right] \in \mathbb{N} ^{d} $ be a multi index.
    The local polynomial space $\mathcal{P} ^{k}( T) $ for a simplex is denoted as
    \begin{equation}
    \label{eq:pol_space}
        \mathcal{P}^{k}( T) =  \mathrm{span}\left\{ x^{\alpha } \ \text{for } x \in T \text{ and } 0 \le  \alpha _{i} \le k \right\}.
    \end{equation}
    where  $x^{\alpha }$ is a monomial such that $x^{\alpha } = x_{1}^{\alpha _{1}} \ldots x_{d}^{\alpha _{d}}$.

    Let $T$ be a cuboid, i.e.,  $T = \prod_{i=1}^{d} [z_{i}^{-},z_{i}^{+}]$ where $z_{i}^{-}< z_{i}^{+}$ for $z_{i}^{\pm} \in \mathbb{R} $. Then the polynomial space $\mathcal{Q}^{k}( T)$  in $\mathbb{R} ^{d}$ is defined as the tensor product of 1-dimensional
    finite elements, i.e.,
      \[
    \mathcal{Q} ^{k}(T)  := \mathcal{P}^{k}( [z_{1}^{-},z_{1}^{+}] ) \otimes \ldots \otimes \mathcal{P}^{k}( [z_{d}^{-},z_{d}^{+}] )
    \]
\end{definition}
For more information about the local polynomial spaces, see \cite[Chapter 6.4, 7.3]{ErnGuermond2021}

Following Ciarlet \cite[pp.93]{ciarlet1991basic}, the abstract definition of a finite element is defined as the triplet $( T, \mathcal{P}, \Sigma ) $.
In our case, $T$ represents either a simplex or a quadrilateral geometry, and $\mathcal{P}$ denotes a finite-dimensional polynomial space consisting of $N$ shape functions $\left\{ \phi_{i} \right\}_{i\in \mathcal{I} } $, where $\mathcal{I} = \left\{
1, \ldots, N \right\} $, as depicted in Definition \ref{def:local_space}.
On the other hand, $\Sigma $ is the so-called dual of $\mathcal{P}$, that is, the set of linear forms $\left\{ \sigma _{i} \right\}_{i \in \mathcal{I} } $ such that. $ \sigma_{j} ( \phi_{i} ) = \delta _{ij}$ and $p( x) = \sum_{i\in \mathcal{I} }^{} \sigma_{i} ( p) p_{i} $.
If there is a set of points $\left\{ a_{i} \right\}_{i \in \mathcal{I} } $  in $T$ such that
$\sigma_{i}( p) = p( a_{i}) \  \forall p \in \mathcal{P}$,  then the triple $( T, \mathcal{P}, \Sigma  ) $ is called a Lagrangian finite element. The set of points $\left\{ a_{i} \right\}_{i \in \mathcal{I} }  $ is called nodes and is associated with the
so-called nodal basis of $\mathcal{P} $ such that  $\phi ( a_{i}) = \delta _{ij} \ \forall i,j  \in \mathcal{I} $

As anticipated, the local node configuration of the polynomial space is influenced by the form of $T$. For the purpose of our discussion, let us represent the polynomial basis for a simplicial element and a quadrilateral
element as $\mathcal{P} ^{k}(T )$ and $\mathcal{Q} ^{k}( T)$, both of polynomial order $k$. In Figure \ref{fig:ill_nodes} is it illustrated for  $k=1,2,3$ in dimension $d=2$ on how the node configuration evolve.

\begin{figure}[h!]
    \centering
    \hfill
    \subfloat[$\mathcal{P}^{1}( T)  $]{
        \begin{tikzpicture}[scale=1.0]
            % Define the coordinates
            \coordinate (A) at (0,0);
            \coordinate (B) at (2,0);
            \coordinate (C) at (1,{sqrt(3)});

            % Draw the triangle
            \fill[blue!30] (A) -- (B) -- (C) -- cycle;
            \draw (A) -- (B) -- (C) -- cycle;

            % Draw the nodes
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
        \end{tikzpicture}
    }
    \hfill
    \subfloat[ $\mathcal{P}^{2}( T)  $]{
        \begin{tikzpicture}[scale=1.0]
            % Define the coordinates
            \coordinate (A) at (0,0);
            \coordinate (B) at (2,0);
            \coordinate (C) at (1,{sqrt(3)});

            % Define the midpoints
            \coordinate (D) at ($(A)!0.5!(B)$);
            \coordinate (E) at ($(B)!0.5!(C)$);
            \coordinate (F) at ($(A)!0.5!(C)$);

            % Draw the triangle
            \fill[blue!30] (A) -- (B) -- (C) -- cycle;
            \draw (A) -- (B) -- (C) -- cycle;

            % Draw the nodes
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
            \fill (D) circle (2pt);
            \fill (E) circle (2pt);
            \fill (F) circle (2pt);
        \end{tikzpicture}
    }
    \hfill
    \subfloat[$\mathcal{P} ^{3}( T)  $ ]{
        \begin{tikzpicture}[scale=1.0]
            % Define the coordinates
            \coordinate (A) at (0,0);
            \coordinate (B) at (2,0);
            \coordinate (C) at (1,{sqrt(3)});

            % Define the additional points along the edges
            \coordinate (D) at ($(A)!0.3333!(B)$);
            \coordinate (E) at ($(B)!0.3333!(C)$);
            \coordinate (F) at ($(C)!0.3333!(A)$);
            \coordinate (G) at ($(A)!0.6667!(B)$);
            \coordinate (H) at ($(B)!0.6667!(C)$);
            \coordinate (I) at ($(C)!0.6667!(A)$);

            % Define the centroid
            \coordinate (J) at (1, {sqrt(3)/3});

            % Draw the triangle
            \fill[blue!30] (A) -- (B) -- (C) -- cycle;
            \draw (A) -- (B) -- (C) -- cycle;

            % Draw the nodes
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
            \fill (D) circle (2pt);
            \fill (E) circle (2pt);
            \fill (F) circle (2pt);
            \fill (G) circle (2pt);
            \fill (H) circle (2pt);
            \fill (I) circle (2pt);
            \fill (J) circle (2pt);
        \end{tikzpicture}
    }
    \\
    \hfill
    \subfloat[$\mathcal{Q}^{1}( T)  $]{
        \begin{tikzpicture}[scale=1.0]
            % Define the coordinates
            \coordinate (A) at (0,0);
            \coordinate (B) at (2,0);
            \coordinate (C) at (2,2);
            \coordinate (D) at (0,2);

            % Draw the square
            \fill[blue!30] (A) -- (B) -- (C) -- (D) -- cycle;
            \draw (A) -- (B) -- (C) -- (D) -- cycle;

            % Draw the nodes
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
            \fill (D) circle (2pt);
        \end{tikzpicture}
    }
    \hfill
    \subfloat[ $\mathcal{Q} ^{2}( T)  $]{
        \begin{tikzpicture}[scale=1.0]
            % Define the coordinates
            \coordinate (A) at (0,0);
            \coordinate (B) at (2,0);
            \coordinate (C) at (2,2);
            \coordinate (D) at (0,2);

            % Define the midpoints
            \coordinate (E) at ($(A)!0.5!(B)$);
            \coordinate (F) at ($(B)!0.5!(C)$);
            \coordinate (G) at ($(C)!0.5!(D)$);
            \coordinate (H) at ($(D)!0.5!(A)$);
            % Define the centroid
            \coordinate (M) at (1, 1);

            % Draw the square
            \fill[blue!30] (A) -- (B) -- (C) -- (D) -- cycle;
            \draw (A) -- (B) -- (C) -- (D) -- cycle;

            % Draw the nodes
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
            \fill (D) circle (2pt);
            \fill (E) circle (2pt);
            \fill (F) circle (2pt);
            \fill (G) circle (2pt);
            \fill (H) circle (2pt);
            \fill (M) circle (2pt);
        \end{tikzpicture}
    }
    % And so on for $\mathcal{P}^{3}( S)  $, $\mathcal{P}^{4}( S)  $, etc.
    \hfill
    \subfloat[ $\mathcal{Q} ^{3}( T)  $]{
        \begin{tikzpicture}[scale=1.0]
            % Define the coordinates
            \coordinate (A) at (0,0);
            \coordinate (B) at (2,0);
            \coordinate (C) at (2,2);
            \coordinate (D) at (0,2);

            % Define the additional points along the edges
            \coordinate (E) at ($(A)!0.3333!(B)$);
            \coordinate (F) at ($(B)!0.3333!(C)$);
            \coordinate (G) at ($(C)!0.3333!(D)$);
            \coordinate (H) at ($(D)!0.3333!(A)$);
            \coordinate (I) at ($(A)!0.6667!(B)$);
            \coordinate (J) at ($(B)!0.6667!(C)$);
            \coordinate (K) at ($(C)!0.6667!(D)$);
            \coordinate (L) at ($(D)!0.6667!(A)$);

            % Define the internal nodes
            \coordinate (M) at ($(E)+(0,0.6667)$);
            \coordinate (N) at ($(E)+(0,1.332)$);
            \coordinate (O) at ($(I)+(0,0.6667)$);
            \coordinate (P) at ($(I)+(0,1.332)$);

            % Draw the square
            \fill[blue!30] (A) -- (B) -- (C) -- (D) -- cycle;
            \draw (A) -- (B) -- (C) -- (D) -- cycle;

            % Draw the nodes
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
            \fill (D) circle (2pt);
            \fill (E) circle (2pt);
            \fill (F) circle (2pt);
            \fill (G) circle (2pt);
            \fill (H) circle (2pt);
            \fill (I) circle (2pt);
            \fill (J) circle (2pt);
            \fill (K) circle (2pt);
            \fill (L) circle (2pt);
            \fill (M) circle (2pt);
            \fill (N) circle (2pt);
            \fill (O) circle (2pt);
            \fill (P) circle (2pt);
        \end{tikzpicture}
        }
        \caption{Illustration of the nodes for the element of a simplex a quadrilateral for dimension $d=2$ for polynomial orders $k=1,2,3$.}
        \label{fig:ill_nodes}
\end{figure}


We may introduce the reference element $\hat{T} $ in $d$ dimensions. The reference for a quadrilateral is denoted as $\hat{T} = [0,1]^{d}$. The reference for a simplex in  is defined by the convex hull spanned by the points $( z_{0}, e_{1}, \ldots, e_{d}) $ where $z_{0}:=0$ is the origin and $ \left\{ e_{i}
\right\}_{i=1}^{d} $ is the standard Cartesian  unit basis in $ \mathbb{R} ^{d} $. A corresponding reference finite element is defined as $( \hat{T}, \hat{\mathcal{P} }, \hat{\Sigma}   ) $.



\begin{figure}[th!]
    \centering
    \hspace{-2.2cm}  % Adjust the space as necessary
    \subfloat[]{
        \begin{tikzpicture}[scale=1.0]
            % Define the Reference triange
            \coordinate (A) at (0,0);
            \coordinate (B) at (1,0);
            \coordinate (C) at (0,1);
            \coordinate (G1) at (1/3,1/3);

            \fill[red!30] (A) -- (B) -- (C) -- cycle;
            \draw (A) -- (B) -- (C) -- cycle;
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);

            % Define the arbitary triange
            \coordinate (D) at (2,0);
            \coordinate (E) at (4,0);
            \coordinate (F) at (3,{sqrt(2)});
            \coordinate (G2) at (3, {sqrt(3)/3});

            \fill[blue!30] (D) -- (E) -- (F) -- cycle;
            \draw (D) -- (E) -- (F) -- cycle;
            \fill (D) circle (2pt);
            \fill (E) circle (2pt);
            \fill (F) circle (2pt);

            % Draw arrow to signify the mapping G
            \draw[->, thick, >=stealth] ($(G1)+(0.2,0.2)$) to[bend left] node[midway, above, yshift=0.1cm] {$\mathcal{G}$} ($(G2)+(-0.2,0.2)$);
        \end{tikzpicture}
    }
    \hspace{2.0cm}  % Adjust the space as necessary
    \subfloat[]{
        \begin{tikzpicture}[scale=1.0]
            % Define the Reference quadrilateral
            \coordinate (A) at (0,0);
            \coordinate (B) at (1,0);
            \coordinate (C) at (1,1);
            \coordinate (D) at (0,1);
            \coordinate (G1) at (0.5,0.5);

            \fill[red!30] (A) -- (B) -- (C) -- (D) -- cycle;
            \draw (A) -- (B) -- (C) -- (D) -- cycle;
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
            \fill (D) circle (2pt);

            % Define the arbitrary quadrilateral
            \coordinate (E) at (2,0);
            \coordinate (F) at (3,1);
            \coordinate (G) at (3,2);
            \coordinate (H) at (2,1);
            \coordinate (G2) at (2.5,0.5);

            \fill[blue!30] (E) -- (F) -- (G) -- (H) -- cycle;
            \draw (E) -- (F) -- (G) -- (H) -- cycle;
            \fill (E) circle (2pt);
            \fill (F) circle (2pt);
            \fill (G) circle (2pt);
            \fill (H) circle (2pt);

            % Draw arrow to signify the mapping G
            \draw[->, thick, >=stealth] ($(G1)+(0.3,0.1)$) to[bend left] node[midway, above, yshift=0.1cm] {$\mathcal{G}$} ($(G2)+(-0.2,0.2)$);
        \end{tikzpicture}
    }
    \\
    \subfloat[]{
        \begin{tikzpicture}[scale=1.0]
            % Define the Reference tetra
            \coordinate (A) at (0,0);
            \coordinate (B) at (1,0);
            \coordinate (C) at (0,1);
            \coordinate (D) at (0.7,0.7);
            \coordinate (G1) at (1/3,1/3);

            \fill[red!65] (A) -- (B) -- (C) -- cycle;
            \fill[red!30] (D) -- (B) -- (C) -- cycle;
            \draw (A) -- (B) -- (C) -- cycle;
            \draw (D) -- (B) -- (C) -- cycle;
            \draw[dashed] (A) -- (D);
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
            \fill (D) circle (2pt);


            % Define the Translated tetra
            \coordinate (A') at ($(A) + (2,0)$);
            \coordinate (B') at ($(B) + (2,0)$);
            \coordinate (C') at ($(C) + (2.6, 0.6)$);
            \coordinate (D') at ($(D) + (2.5, 0.2)$);

            \fill[blue!65] (A') -- (B') -- (C') -- cycle;
            \fill[blue!30] (D') -- (B') -- (C') -- cycle;
            \draw (A') -- (B') -- (C') -- cycle;
            \draw (D') -- (B') -- (C') -- cycle;
            \draw[dashed] (A') -- (D');
            \fill (A') circle (2pt);
            \fill (B') circle (2pt);
            \fill (C') circle (2pt);
            \fill (D') circle (2pt);

            % Draw arrow to signify the mapping G
            \draw[->, thick, >=stealth] ($(G1)+(0.6,0.2)$) to[bend left] node[midway, above, yshift=0.1cm] {$\mathcal{G}$} ($(D')+(-0.6,0.1)$);
        \end{tikzpicture}
    }
    \hspace{2cm}  % Adjust the space as necessary
    \subfloat[]{
        \begin{tikzpicture}[scale=1.0]
    % Define the Reference cube
    \coordinate (A) at (0,0);
    \coordinate (B) at (1,0);
    \coordinate (C) at (1,1);
    \coordinate (D) at (0,1);
    \coordinate (E) at (0.3,0.3);
    \coordinate (F) at (1.3,0.3);
    \coordinate (G) at (1.3,1.3);
    \coordinate (H) at (0.3,1.3);

    \fill[red!65] (A) -- (B) -- (C) -- (D) -- cycle;
    \fill[red!45] (D) -- (H) -- (G) -- (C) -- cycle;
    \fill[red!30] (B) -- (C) -- (G) -- (F) -- cycle;
    \draw (A) -- (B) -- (C) -- (D) -- cycle;
    \draw (A) -- (E) -- (F) -- (B);
    \draw (D) -- (H) -- (G) -- (C);
    \draw[dashed] (E) -- (H);
    \draw[dashed] (F) -- (G);

    % Define the Translated cube
    \coordinate (A') at ($(A) + (3.3, 0.0)$);
    \coordinate (B') at ($(B) + (3.3, 0.0)$);
    \coordinate (C') at ($(C) + (3.3, 0.0)$);
    \coordinate (D') at ($(D) + (3.3, 0.0)$);
    \coordinate (E') at ($(E) + (2.2, 0.3)$);
    \coordinate (F') at ($(F) + (2.2, 0.3)$);
    \coordinate (G') at ($(G) + (2.2, 0.3)$);
    \coordinate (H') at ($(H) + (2.2, 0.3)$);

    \fill[blue!65] (A') -- (B') -- (C') -- (D') -- cycle;
    \fill[blue!30] (D') -- (H') -- (G') -- (C') -- cycle;
    \fill[blue!45] (D') -- (A') -- (E') -- (H') -- cycle;
    \draw (A') -- (B') -- (C') -- (D') -- cycle;
    \draw (A') -- (E') -- (F') -- (B');
    \draw (D') -- (H') -- (G') -- (C');
    \draw[dashed] (E') -- (H');
    \draw[dashed] (F') -- (G');

    \fill (A') circle (2pt);
    \fill (B') circle (2pt);
    \fill (C') circle (2pt);
    \fill (D') circle (2pt);
    \fill (E') circle (2pt);
    \fill [opacity=0.5] (F') circle (2pt);
    \fill (G') circle (2pt);
    \fill (H') circle (2pt);

    \fill (A) circle (2pt);
    \fill (B) circle (2pt);
    \fill (C) circle (2pt);
    \fill (D) circle (2pt); % D has half opacity now
    \fill [opacity=0.5](E) circle (2pt);
    \fill (F) circle (2pt);
    \fill (G) circle (2pt);
    \fill (H) circle (2pt);

    % Draw arrow to signify the mapping G
    \draw[->, thick, >=stealth] ($(A)+(0.8,0.5)$) to[bend left] node[midway, above, yshift=0.1cm] {$\mathcal{G}$} ($(A')+(-0.5,0.8)$);
\end{tikzpicture}
    }
    \caption{Illustration of affine mapping $\mathcal{G} : \hat{T} \to T $ in dimensions $d=2,3$ from a reference element $\hat{T}$  to element $T$ for simplexes and and quadrilaterals.  } \label{fig:affine_mapping}
\end{figure}

Let the mapping $\mathcal{G} : \hat{T} \to  T$ an affine
mapping, i.e. $\mathcal{G}(x) = Ax +
b$.
The important property of affine transformations is the preservation of parallelism. Hence,  for any two vectors $x,y \in  \hat{T}$ that are parallel in the reference element, their images $\mathcal{G}(x)  $  and $\mathcal{G}( y)  $ will
also be parallel. Generally speaking, an affine transformation of the reference simplex is a transformation to any another simplex of the same dimension. However, for any quadrilateral, an affine transformation preserves the parallelism of opposite
sides, for an illustration see Figure \ref{fig:affine_mapping} and for a counter example see Figure \ref{fig:nonaffine}.

\begin{figure}[h!]
    \centering
    \hspace{-2.2cm}  % Adjust the space as necessary
    \subfloat[]{
        \begin{tikzpicture}[scale=1.0]
            % Define the Reference quadrilateral
            \coordinate (A) at (0,0);
            \coordinate (B) at (1,0);
            \coordinate (C) at (1,1);
            \coordinate (D) at (0,1);
            \coordinate (G1) at (0.5,0.5);

            \fill[red!30] (A) -- (B) -- (C) -- (D) -- cycle;
            \draw (A) -- (B) -- (C) -- (D) -- cycle;
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
            \fill (D) circle (2pt);

            % Define the arbitrary quadrilateral
            \coordinate (E) at (2,0);
            \coordinate (F) at (3,0);
            \coordinate (G) at (3.5,1);
            \coordinate (H) at (2.5,1);
            \coordinate (G2) at (2.5,0.5);

            \fill[blue!30] (E) -- (F) -- (G) -- (H) -- cycle;
            \draw (E) -- (F) -- (G) -- (H) -- cycle;
            \fill (E) circle (2pt);
            \fill (F) circle (2pt);
            \fill (G) circle (2pt);
            \fill (H) circle (2pt);

            % Draw arrow to signify the mapping G
            \draw[->, thick, >=stealth] ($(G1)+(0.3,0.1)$) to[bend left] node[midway, above, yshift=0.1cm] {$\mathcal{G}$} ($(G2)+(-0.2,0.2)$);
        \end{tikzpicture}
    }
    \hspace{2.0cm}  % Adjust the space as necessary
    \subfloat[]{
        \begin{tikzpicture}[scale=1.0]
            % Define the Reference quadrilateral
            \coordinate (A) at (0,0);
            \coordinate (B) at (1,0);
            \coordinate (C) at (1,1);
            \coordinate (D) at (0,1);
            \coordinate (G1) at (0.5,0.5);

            \coordinate (R1) at (1.5,0.7);
            \coordinate (R2) at (1.4,1.0);

            \fill[red!30] (A) -- (B) -- (C) -- (D) -- cycle;
            \draw (A) -- (B) -- (C) -- (D) -- cycle;
            \draw[very thick] (R1) -- (R2);
            \fill (A) circle (2pt);
            \fill (B) circle (2pt);
            \fill (C) circle (2pt);
            \fill (D) circle (2pt);

            % Define the arbitrary quadrilateral
            \coordinate (E) at (2,0);
            \coordinate (F) at (3.5,0);
            \coordinate (G) at (3.0,1);
            \coordinate (H) at (2.5,1);
            \coordinate (G2) at (2.5,0.5);

            \fill[blue!30] (E) -- (F) -- (G) -- (H) -- cycle;
            \draw (E) -- (F) -- (G) -- (H) -- cycle;
            \fill (E) circle (2pt);
            \fill (F) circle (2pt);
            \fill (G) circle (2pt);
            \fill (H) circle (2pt);

            % Draw arrow to signify the mapping G
            \draw[->, thick, >=stealth] ($(G1)+(0.3,0.1)$) to[bend left] node[midway, above, yshift=0.1cm] {$\mathcal{G}$} ($(G2)+(-0.2,0.2)$);

        \end{tikzpicture}
    }
    \caption{Illustration of an affine mapping $\mathcal{G}: \hat{T} \mapsto T$  versus a non-affine transformation. The left figure preserves parallel lines before and after the transformation, indicating an affine transformation. However, the right figure does not maintain parallelism, making it a non-affine transformation.}
    \label{fig:nonaffine}
\end{figure}

Following \cite[Example 9.4]{ErnGuermond2021}, the $ ( \hat{T}, \hat{\mathcal{P} }, \hat{\Sigma} ) $ is denoted as the reference finite element associated with the nodes $\left\{ \hat{a}_{i} \right\}_{i\in N} $. Let the mapping $\psi $ be function in $\mathcal{L}( \mathcal{P} ^{k}( T), \mathcal{P} ^{k}(\hat{T}
)  )  $ such that is an isomorphic from  $ \psi : \mathcal{P} ^{k}( T) \to \mathcal{P} ^{k}( \hat{T})   $.  Then $\sigma ( p) = \hat{\sigma }( \psi ( p) ) (a_{i} )  = ( p \circ \mathcal{G} )( \hat{a}_{i})      $ for all $p \in \mathcal{P}^{k}( T)  $.
Then the Lagrange interpolation follows,  \[
    p (x) = \sum_{i \in N }^{} \sigma ( a_{i}) \phi_{i}( x) \quad \text{for } a_{i} = \mathcal{G}( \hat{a}_{i}) \quad  \forall i \in N     .
\]
Hence, the finite element $( T, \mathcal{P}, \Sigma  ) $, associated with the notes $\left\{ a_{i} \right\}_{i\in N} $, is reconstructed via the reference finite element $( \hat{T}, \hat{\mathcal{P} }, \hat{\Sigma} ) $.
Thus, using the affine transformation can the definition of the local polynomial space be extended to dependent on the reference element. That is, \[
    \begin{split}
\mathcal{P}^{k}( T) & = \left\{ \hat{v} \circ  \mathcal{G}^{-1}( T)   \mid  \hat{v} \in \mathcal{P}^{k}( \hat{T})      \right\} \\
\mathcal{Q}^{k}( T) & = \left\{ \hat{v} \circ  \mathcal{G}^{-1}( T)     \mid  \hat{v} \in \mathcal{Q}^{k}( \hat{T})      \right\} \\
    \end{split}
\]
Working on shape-regular and affine geometries has shown to greatly simplify and generalise local interpolation estimates, see \cite[Theorem 11.12]{ErnGuermond2021}, and thus is very useful for deriving a priori estimates.
Please note that workarounds exist for proving nonaffine local interpolation estimates, but they require key assumptions on the relationship between the nodes $a_{i}$ and the regularity of the mapping $\mathcal{G} $ \cite[Chapter 13]{ErnGuermond2021}.
Hence, affine meshes is essential for the error analysis which utilize the interpolation estimates, but it limits us to work on structure mesh if we specifically choose on quadrilateral meshes.

\begin{definition}[Broken polynomial spaces]
    Let $\mathcal{T}_{h} $ be a mesh of $\Omega \in \mathbb{R} ^{d} $ and $\Omega _{h} = \bigcup_{T \in \mathcal{T}_{h} } T$ . Let $\mathcal{P}^{k}(T) $ be the space of all polynomials of order $k$ in the mesh element $T$ in $\mathcal{T}_{h}$ . We define the broken polynomial space and the global $C^{0}$ continuous polynomial space as
    \begin{equation}
        \begin{split}
    \mathcal{P}^{k} ( \mathcal{T}_{h} ) & := \left\{ v \in L^{2}( \Omega _{h} )    \mid  v|_{T} \in \mathcal{P}^k( T) \quad  \forall T \in  \mathcal{T}_{h}   \right\}. \\
    \mathcal{P}^{k}_{c} ( \mathcal{T}_{h} ) & := \left\{ v \in C^{0}( \Omega _{h}  )   \mid  v|_{T} \in \mathcal{P}^k( T) \quad  \forall T \in  \mathcal{T}_{h}   \right\}.
        \end{split}
    \end{equation}
    Similarly, for quadrilatural elements is the polynomial spaces defined as,
    \begin{equation}
        \begin{split}
    \mathcal{Q}^{k} ( \mathcal{T}_{h} ) & := \left\{ v \in L^{2}( \Omega _{h} )    \mid  v|_{T} \in \mathcal{Q}^k( T) \quad  \forall T \in  \mathcal{T}_{h}   \right\}. \\
    \mathcal{Q}^{k}_{c} ( \mathcal{T}_{h} ) & := \left\{ v \in C^{0}( \Omega _{h} )   \mid  v|_{T} \in \mathcal{Q}^k( T) \quad  \forall T \in  \mathcal{T}_{h}   \right\}.
        \end{split}
    \end{equation}

\end{definition}


In this thesis will we generally utilize the global $C^{0}$ continuity, hence, for the rest of the thesis do we define
\begin{equation}
    \label{def:Vh_background}
V_{h} =  \left\{ P_{c}^{k}( \mathcal{T}_{h} ) \text{ or }  Q_{c}^{k}( \mathcal{T}_{h} )
 \right\} \end{equation}
Hence, all results holds for both polynomial spaces.

\begin{figure}[h!]
\centering
\begin{tikzpicture}[node distance=2cm,
                    box1/.style={rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=red!30},
                    box2/.style={rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30},
                    box3/.style={rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30},
                    box4/.style={rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30},
                    arrow/.style={thick,->,>=stealth}
                    ]
\node (sf) [box1] { Find $u:\Omega \to \mathbb{R} $ such that $\mathcal{A} u = f$};
\node[left=0.5cm of sf,font=\bfseries, align=right] {Strong formulation:};

\node (alp) [box2, below of=sf] {Find $u \in V$ such that $a(u,v) = l(v) \  \forall v \in V$};
\node[left=0.5cm of alp,font=\bfseries, align=right] {Abstract weak problem:};

\node (dlp) [box3, below of=alp] {Find $u_h \in V_{h}$ such that $a_{h}(u_h,v_h) = l_h(v) \  \forall v_h \in V_{h}$};
\node[left=0.5cm of dlp,font=\bfseries, align=right] {Discrete weak problem:};

\node (lse) [box4, below of=dlp] {Solve $A U = F$};
\node[left=0.5cm of lse,font=\bfseries, align=right] {Linear system of equations:};

\draw [arrow] (sf) -- (alp);
\draw [arrow] (alp) -- (dlp);
\draw [arrow] (dlp) -- (lse);
\end{tikzpicture}
\caption{Workflow of solving linear PDEs using the FEM method.}
\label{fig:fem_workflow}
\end{figure}

We now have a well-defined discrete global space  $V_{h} $ consisting of the finite set of basis functions $\left\{ \phi _{i} \right\}_{i=1}^{N} $ associated with the Lagriangian nodes $\left\{ a_{i} \right\}_{i=1}^{N}  $. The degree of freedoms,
also known as ndofs, is denoted as $dim(V_{h}) = N$. Let $U_{j} = u_{h}\left(
a_{j} \right) $, so that $u_{h} = \sum_{j=1}^{N} U_{j} \phi _{j}  $. Then the Problem \ref{def:approx_problem} is equivalent to
\begin{equation}
    \label{eq:discretized_system}
\sum_{j = 1}^{N} u_{j} a_{h}\left( \phi _{j}, \phi _{i} \right)  = l_{h}\left( \phi _{i} \right)
\end{equation}
Hence, by letting $U = \left[ U_{j} \right] $ , $F = \left[ \left( f, \phi _{i}  \right) _{\Omega } \right] $  and $A = \left[ a_{h}\left( \phi _{j}, \phi _{i} \right)  \right] $ can we construct a linear system,
\begin{equation}
\label{eq:linear_system}
    A U =F.
\end{equation}
Ultimately, the matrix $A$ is shown to be symmetric positive definite only if $a_{h}( \cdot ,\cdot ) $ is well-posed.


To summarize the workflow of solving linear PDEs using the FEM method, see Figure \ref{fig:fem_workflow}.

\subsection{Condition number}%
\label{sub:note_on_condition_number}

Recall the discrete $l^{p}$ norm for a vector,

 \begin{equation}
     \forall U \in \mathbb{R} ^{N}, \quad
\| U  \|_{ p }^{  } =
     \begin{cases}
     &  \left( \sum_{i=1}^{N}  \abs{ U_{i}  }^{p} \right)^{\frac{1}{p}} , \quad  1\le p < \infty \\
   &  \max_{i}  \abs{ U_i },  \quad  p= \infty
     \end{cases}
 \end{equation}
Also recall the definition of the matrix norm,
\begin{equation}
 \forall A \in \mathbb{R} ^{N\times N}, 1\le p \le  \infty, \quad  \| A  \|_{p  }^{  }  = \max_{U \in \mathbb{R} ^{N} \setminus 0} \frac{\| AU \|_{ p }^{  } }{\| U \|_{p}^{  } }.
\end{equation}
Remark that this notation is not to be confused with Sobolev norms.
Assume that $A $ is invertible, then we define the condition number for a matrix in $l^{p}  $ norm defined such that
\begin{equation}
    \label{eq:condition_num}
 \forall A \in \mathbb{R} ^{N\times N}, 1\le p \le  \infty, \quad  \kappa_{p} ( A) = \| A  \|_{ p }^{  } \| A ^{-1} \|_{ p }.
\end{equation}

From basic theory is it known that $\| A \|_{ 2 }^{  } $   is equal to the maximum singular value of $A$ , where singular values of $ A$  are the square roots of the eigenvalues of $A^TA$ \cite[Theorem 2.9]{ suli2003introduction}. Because of the connection
between $\| A \|_{ 2 }^{  } $ norms and its singular values, is $k_{2}( A) $ is often in preferred numerical analysis.
A challenge is that the computations generally involves performing Singular Value Decomposition (SVD)
 or power iteration, which can be quite expensive operations particularly for large sparse matrices.
 However,  $\| A \|_{ \infty }^{  } $ is computed as the maximum absolute row sum and ,hence, only necessary to compute the sum for the non-zero elements in each row. Thus, we seek to estimate
 $\kappa_{2}( A) $ using $ \kappa _{\infty}( A) $.

It is well established that $ \frac{1}{\sqrt{N} }  \| A \|_{ \infty }^{  }  \le \| A \|_{2  }^{  } \le
\sqrt{N}  \| A \|_{\infty  }^{  }  $ for any matrix $A \in R^{N\times N}$  \footnote{
    The identity naturally appears from the standard inequality $\| v \|_{ \infty }^{  } \le  \| v \|_{2  }^{  } \le \sqrt{N}  \| v \|_{ \infty }^{  }   $ for $v \in R^{N}$, which simply comes from the fact that  $ \| v \|_{\infty  }^{ 2 } = \max_{i} \abs{ v_{i} }^{2} \le \sum_{i}^{n}   \abs{ v_{i} }^{2} = \| v \|_{ 2 }^{2  } \le N      \max_{i} \abs{ v_{i} }^{2} = N \| v \|_{
    \infty}^{ 2 }$. Now let $A\in \mathbb{R} ^{N \times N}$ be any matrix. We can then deduce that $ \| A \|_{ 2 }^{  } = \max_{v \in \mathbb{R} ^{N}} \frac{\| Av \|_{2  }^{  }}{\| v \|_{ 2 }^{  } } \ge \max_{v \in \mathbb{R} ^{N}}
    \frac{\| Av \|_{ \infty  }^{  }}{ \sqrt{N} \| v \|_{ \infty}^{  } } = \frac{1}{ \sqrt{N} } \| A \|_{ \infty }^{  }    $ and $ \| A \|_{ 2 }^{  } = \max_{v \in \mathbb{R} ^{N}} \frac{\| Av \|_{2  }^{  }}{\| v \|_{ 2 }^{  } } \le  \max_{v \in \mathbb{R} ^{N}}
    \frac{\sqrt{N} \| Av \|_{ \infty  }^{  }}{  \| v \|_{ \infty}^{  } } =  \sqrt{N} \| A \|_{ \infty }^{  }    $. Hence, the identity $\frac{1}{\sqrt{N} } \| A \|_{\infty  }^{  } \le \| A \|_{ 2 }^{  }\le \sqrt{N} \| A \|_{ \infty  }^{  }   $  is proven.

}. Applying this identity, we obtain the upper and lower bounds for $\kappa_{2}(A)$. Specifically, we have
\begin{equation}
\frac{1}{N} \kappa_{\infty} ( A) \le  \kappa_{2} ( A) \le N \kappa _{\infty}(A)
\end{equation}
Thus, since these norms are equivalent, will we in this thesis focus on $ \kappa_{\infty}( A)  $ because of the efficiency of computing $\| A \|_{ \infty }^{  } $  .

\subsection{Cléments interpolation}%
\label{ssub:clement_operator}
Our goal is to to utilize interpolation estimates to compute convergence rates. An important tool in the process is the so-called Cléments interpolation operator, $C_{h}$.
It is used for interpolation on non smooth functions by applying an regularization on so-called macroelements. However, we need to define affine operations on so-called macroelements before we can proceed with the error estimates.

A patch for a element $\omega \left( T \right) $ is denoted as the set of elements in $\mathcal{T} _{h}$  sharing at least one vertex with $T \in \mathcal{T} _{h}$. Similarly,  a patch of a facet $\omega \left( F \right) $ is defined as the set of all elements in $\mathcal{T}_{h} $
sharing at least one vertex with $F \in  \mathcal{F} _{h}$. For an illustrative example of patches in a two-dimensional triangular mesh, please refer to Figure \ref{fig:example_patch}.

\begin{figure}[ht!]
    \centering

  \centering
    \subfloat{{
    \begin{minipage}[b]{0.45\textwidth}
        \begin{tikzpicture}
            % Define the coordinates
            \coordinate (A) at (0,0);
            \coordinate (B) at (2,0);
            \coordinate (C) at (1,2);
            \coordinate (D) at (2.5,2);
            \coordinate (F) at (1.5,3);
            \coordinate (E) at (-1,2);
            \coordinate (G) at (1,-2);
            \coordinate (H) at (2.5,-2);
            \coordinate (I) at (4,-1);

            \fill[blue!30] (A) -- (G)-- (H) -- (I)  -- (D) -- (F)-- (E)   -- cycle;

            % Draw the triangle
            \draw (A) -- (G)-- (H) -- (I)  -- (D) -- (F)-- (E)   -- cycle;
            \draw (A) -- (C);
            \draw (A) -- (B);
            \draw (G) -- (B);
            \draw (I) -- (B);
            \draw (F) -- (C);
            \draw (H) -- (B);
            \draw (D) -- (C);
            \draw (D) -- (B);
            \draw (E) -- (C);
            \draw[line width=2pt] (B) -- (C);
            \node at (1.6,1.3) {$F$};

        \end{tikzpicture}
    \end{minipage}\hfill

}}%
    \qquad
    \subfloat{{

    \begin{minipage}[b]{0.45\textwidth}
        \begin{tikzpicture}
                    % Define the coordinates
        \coordinate (A) at (0,0);
        \coordinate (B) at (2,0);
        \coordinate (C) at (1,2);
        \coordinate (D) at (2.5,2);
        \coordinate (F) at (1.5,3);
        \coordinate (E) at (-1,2);
        \coordinate (G) at (1,-2);
        \coordinate (H) at (2.5,-2);
        \coordinate (I) at (4,-1);
        \coordinate (K) at (-2,-0.3);

        \fill[blue!30] (K) -- (G)-- (H) -- (I)  -- (D) -- (F)-- (E)   -- cycle;
        % \fill[red!30] (B) -- (C) -- (A);

        % Draw the triangle
        \draw (A) -- (G)-- (H) -- (I)  -- (D) -- (F)-- (E)   -- cycle;
        \draw (A) -- (C);
        \draw (A) -- (B);
        \draw (G) -- (B);
        \draw (I) -- (B);
        \draw (F) -- (C);
        \draw (H) -- (B);
        \draw (D) -- (C);
        \draw (D) -- (B);
        \draw (E) -- (C);
        \draw (K) -- (A);
        \draw (K) -- (G);
        \draw (K) -- (E);
        \draw[line width=2pt] (B) -- (C) -- (A) -- cycle;
        \node at (1.0,1.0) {$T$};

        \end{tikzpicture}
    \end{minipage}

    }}%
\caption{Illustration of the patch $\omega ( F) $ on the left-hand side and $\omega(T)$ on the right-hand side.}
    \label{fig:example_patch}%
\end{figure}

\begin{figure}[]
\begin{minipage}{.5\linewidth}
\centering
\subfloat[]{
    \label{fig:macroelements:a}
    \begin{tikzpicture}[scale=0.5]
        % Arbitrary triangle
        \coordinate (A1) at (0,0);
        \coordinate (B1) at (4,1);
        \coordinate (C1) at (1,3);
        \fill [blue!30] (A1) -- (B1) -- (C1) -- cycle;
        \draw (A1) -- (B1) -- (C1) -- cycle;

        % Centroid
        \coordinate (ai) at (barycentric cs:A1=1,B1=1,C1=1);
        \fill (ai) circle (2pt);
        \node[anchor=north east] at (ai) {$a_i$};

        % Reference triangle
        \coordinate (A2) at ($(A1) + (6, 0)$);
        \coordinate (B2) at ($(A2) + (0, 3)$);
        \coordinate (C2) at ($(A2) + (3, 0)$);
        \fill [red!30] (A2) -- (B2) -- (C2) -- cycle;
        \draw (A2) -- (B2) -- (C2) -- cycle;

        % Centroid of the reference triangle
        \coordinate (ahi) at (barycentric cs:A2=1,B2=1,C2=1);
        \fill (ahi) circle (2pt);
        \node[anchor=north west, xshift=-0.1cm, yshift=0.1cm] at (ahi) {$\hat{a}_{j( i)} $};

        \draw[->, thick, >=stealth] ($(ahi)+(0.2,+0.2)$) to[bend right] node[midway, above] {$\mathcal{G}_{A_i}$} ($(ai)+(0.2,+0.3)$);

    \end{tikzpicture}
}
\end{minipage}%
\begin{minipage}{.5\linewidth}
\centering
\subfloat[]{
    \label{fig:macroelements:b}
    \begin{tikzpicture}[scale=0.5]
    % Arbitrary square
    \coordinate (A1) at (0,0);
    \coordinate (B1) at (3,1);
    \coordinate (C1) at (4,4);
    \coordinate (D1) at (1,3);
    \fill[blue!30] (A1) -- (B1) -- (C1) -- (D1) -- cycle;
    \draw (A1) -- (B1) -- (C1) -- (D1) -- cycle;

    % Draw edge from D1 to B1
    \draw (D1) -- (B1);

    % Pick a point on the edge and label it as a_i
    \coordinate (a_i) at ($(D1)!.6!(B1)$);
    \fill (a_i) circle (2pt);
    \node[anchor=north] at (a_i) {$a_i$};

    % Reference equilateral triangle
    \coordinate (A2) at ($(A1) + (6, 0)$);
    \coordinate (B2) at ($(A2) + (2, 3.464)$); % 3.464 = 2 * sqrt(3)
    \coordinate (C2) at ($(A2) + (4, 0)$);
    \fill[red!30] (A2) -- (B2) -- (C2) -- cycle;
    \draw (A2) -- (B2) -- (C2) -- cycle;

    % Divide the equilateral triangle into two right triangles
    \coordinate (M) at ($(A2)!.5!(C2)$);
    \draw (B2) -- (M);

    % Pick a point on the shared edge and label it as ahat_i
    \coordinate (ahat_i) at ($(B2)!.7!(M)$);
    \fill (ahat_i) circle (2pt);
    \node[anchor=north west] at (ahat_i) {$\hat{a}_{j( i)} $};

    % Draw the mapping G_{A_i} from ahat_i to a_i
    \draw[->, thick, >=stealth] ($(ahat_i)+(0.2,0.2)$) to[bend right] node[midway, above] {$\mathcal{G}_{A_i}$} ($(a_i)+(0.2,0.2)$);
\end{tikzpicture}
}
\end{minipage}\par\medskip
\centering
\subfloat[]{
    \label{fig:macroelements:c}
 \begin{tikzpicture}[scale=0.5]

    % Central vertex a_i
    \coordinate (ah_i) at (0, 0);

    % Reference hexagon
    \foreach \angle in {0, 60, ..., 300} {
        \coordinate (A) at (\angle:2.5);
        \coordinate (B) at (\angle + 60:2.5);
        \fill[red!30] (ah_i) -- (A) -- (B) -- cycle;
        \draw (ah_i) -- (A) -- (B) -- cycle;
    }

    \fill (ah_i) circle (2pt);
    \node[anchor=east, yshift=0.25cm] at (ah_i) {$\hat{a}_{j( i) }$};

    \coordinate (A1) at (5, 0);
    \coordinate (B1) at (8, 0);
    \coordinate (C1) at (8, 3);
    \coordinate (D1) at (7, 4);
    \coordinate (E1) at (3.5, 4);
    \coordinate (F1) at (3, 2);
    \fill[blue!30] (A1) -- (B1) -- (C1) -- (D1) -- (E1) -- (F1) -- cycle;
    \draw (A1) -- (B1) -- (C1) -- (D1) -- (E1) -- (F1) -- cycle;

    \coordinate (ai) at (barycentric cs:A1=1,B1=1,C1=1,D1=1,E1=1,F1=1);
    % Draw lines from vertices to a_i
    \draw (A1) -- (ai);
    \draw (B1) -- (ai);
    \draw (C1) -- (ai);
    \draw (D1) -- (ai);
    \draw (E1) -- (ai);
    \draw (F1) -- (ai);
    % Centroid
    \fill (ai) circle (2pt);
    \node[anchor=south, yshift=0.2cm] at (ai) {$a_i$};

    \draw[->, thick, >=stealth] ($(ah_i)+(0.2,- 0.2)$) to[bend right] node[midway, above, yshift=0.1cm] {$\mathcal{G}_{A_i}$} ($(ai)+(-0.2,-0.2)$);

\end{tikzpicture}
}

\caption{Illustration of the different cases when mapping from the reference macroelement $\widehat{A}_{j( i) }$  to the domain $A_{i}$,  $\mathcal{G} _{A_{i}}: \widehat{A}_{j( i) } \to A_{i}$. Here we have defined $\hat{a}_{j(i)} \in
    \widehat{A}_{j(i)}$ s.t. $\mathcal{G}_{A_{i}} ( \hat{a}_{j( i) }) = a_i$. }

\label{fig:macroelements}
\end{figure}


 Let the set  $\left\{ a_{i}\right\}_{i\in N}$ be all Lagrange nodes on the mesh $\mathcal{T}_{h}$. Associated with each node $a_{i}$ we denote the macroelement $A_{i}$ to consist of all elements containing $a_{i}$. Let $n_{cf}$ be the number of configurations for the macroelement, then we define the index $j:
\left\{ 1,\ldots,N \right\} \to \left\{ 1, \ldots, n_{cf} \right\}  $ s.t. $j( i) $ is the index associated with the reference configuration $\widehat{A}_{j(i) }$ for corresponding macroelement $A_{i}$.
Let us define a $C^{0}$-diffeomorphism $\mathcal{G}_{A_{i}}:
\widehat{A}_{j( i) } \to A_{i}$ on the reference macroelements such that for all $\hat{T} \in \widehat{A}_{j( i) } $ is the restriction $\mathcal{G} _{A_{i}}|_{ \hat{T} }$ affine. For an illustration of the reference
macroelement $\widehat{A}_{j( i) }$ and how it related to $a_{i}$ , see
Figure \ref{fig:macroelements}.

The Cléments interpolation operator $C_{h}$ is the $L^2$-projection onto the macroelements. That is, given
a reference macroelement $\widehat{A}_{j( i) }$ and a function $\hat{v} \in L^{1}( \widehat{A}_{j( i) })  $, then $\widehat{C}_{j( i) } \hat{v}$  is the unique polynomial in $\mathcal{P}^{k} ( \widehat{A}_{j( i) })  $ s.t. \[
\int_{  \widehat{A}_{j( i) }}^{} ( \widehat{C}_{j( i) } \hat{v} - \hat{v}) p \ dx  = 0 \quad  \forall p \in \mathcal{P}^{k} ( \widehat{A}_{j( i) })
\]
Finally, the Cléments interpolator is defined as the mapping $C_{h} : L^{1}( \Omega )  \to \mathcal{P} ^{k}_{c}(\mathcal{T}_{h}   ) $ such that
\[
C_{h} v = \sum_{i=1}^{N} \widehat{C}_{j( i) } ( v (\mathcal{G} _{A_{i}}) (\mathcal{G}^{-1}_{A_{i}}(a_{i})) )\phi _{i},
\]
where $\phi _{i}$ is the corresponding polynomial basis associated with the node $a_{i}$.

% Recall the general Sobolev norm notation,
% \[
% \| u \|_{ m,p,T }^{  } = \left( \sum_{ \left\lvert \alpha  \right\rvert \le m}^{} \int_{T}^{}  \left\lvert  \partial ^{\alpha } u \right\rvert^{p} dx   \right)^{\frac{1}{2}}
% \]
% where we use the convenient notation $\| u \|_{L^2(T) }^{  } = \| u \|_{ T  }^{  } = \| u \|_{ 0,2,T  }^{  } $ and similarly $\| u \|_{ H^r( T )  }^{  } = \| u \|_{ r,T  }^{  } = \| u \|_{ r,2,T  }^{  }  $.


Finally, we have the following a priori estimate.

\begin{lemma}
    \label{lemma:clements}

    Let $v \in H^{s}( \Omega ) $. We define the Clement interpolation as the mapping
$C_{h}: L^{2}( \Omega )   \to  V_{h}$, where $V_{h}$ has the order $k$. Then does the following stability estimate hold,
\[
 \| C_{h} v \|_{ s, \Omega     }^{  } \lesssim \| v \|_{ s, \Omega   }^{  } \quad \forall v \in H^{s}( \Omega ) ,
\]
Let $r = \mathrm{min} ( s, k+1) $. If the following conditions for an parameter $l$ is satisfied, it exists error estimates such that
\begin{equation}
    \begin{split}
      0\le l \le r  \implies \| v - C_{h} v \|_{ m,T   }^{  }  &  \lesssim h^{r-l}_{T} \| v \|_{l,\omega \left( T \right)  }^{  } \quad  \forall T \in \mathcal{T} _{h}, \forall v \in H^{l}( \omega \left( T \right)
      ), \\
      0\le l \le r-\frac{1}{2}  \implies \| v - C_{h} v \|_{ m,F }^{  } & \lesssim h^{r - l - \frac{1}{2}}_{T} \| v \|_{l,\omega \left( F \right)  }^{  } \quad  \forall \partial T \in \mathcal{T} _{h}, \forall v \in H^{l}( \omega \left( F
      \right)).
    \end{split}
\end{equation}

\end{lemma}


\begin{corollary}
    \label{cor:celement_apriori}
    Let $0 \le l \le k+1$ and let $0\le m \le \min_{} ( 1,l )$.
    Given Lemma \ref{lemma:clements}  then does the following estimate hold
    \[
    \inf_{v_{h} \in V_{h} } \| v - v_{h} \|_{  m,\Omega }^{  } \lesssim   h^{l-m}  \| v \|_{ l,\Omega  }^{  } \quad     \forall v \in H^{l}( \Omega ).
    \]
\end{corollary}
This result is very useful since it is now sufficient to show that a priori estimates holds to prove convergence rate. For further detailed information about the Cléments interpolation, please investigate \cite[Chapter 1.6]{ern04}.

\subsection{Useful local inverse estimates}%
\label{sub:some_general_inequalities}


    Choose any element $T \in \mathcal{T}_{h} $ and let $v_{h} \in \mathcal{P} ^{m}( T)   $. Then does the local inverse estimate hold,
\begin{equation}
\label{eq:inv1}
\abs{ v_{h} }_{H^{l}( T) }  \lesssim h^{m-l} \abs{ v_{h} }_{H^{m}( T  ) }
\text{ for } l \le m.
\end{equation}
 For proof, see \cite[Lemma 12.1]{ErnGuermond2021}. An essential example is the following inequality.
 \begin{equation}
     \label{eq:degrade}
\| D^2v_{h} \|_{T  }^{  } \lesssim h^{-1} \| \nabla v_{h}  \|_{ T  }^{  } \lesssim h^{-2} \| v_{h} \|_{T  }^{  }
 \end{equation}

Another very useful inequality is the so-called trace inequality which connect the relationship of evaluating the norm on element $ T $ and with any of the corresponding facets $F \in \partial T$. The general form is
\begin{equation}
    \label{eq:inv2}
\| v_{h} \|_{F   }^{  }  \lesssim
h^{-\frac{1}{2}} \| v_{h} \|_{ T  }^{  },
\end{equation}
For proof, see \cite[Lemma 12.8]{ErnGuermond2021}.

Let $\partial _{n} v = \nabla v \ n$ and $\partial_{nn} v = n^{T} D^2 v \ n $. Keeping in mind that the normal vector has a unit length and, thus, evidently applying the
trace inverse inequality we have two present useful examples,
\begin{equation}
    \label{eq:fund_inv_est}
\begin{split}
    \| \partial _{n} v_{h} \|_{F  }^{  }  & \le \| \nabla v_{h} \|_{F  }^{  }  \le h^{-\frac{1}{2}} \| \nabla  v_{h} \|_{T  }^{  },  \\
    \| \partial _{nn} v_{h} \|_{ F }^{  } & \le  \| D^2 v_{h} \|_{ F }^{  }   \le  h^{-\frac{1}{2}} \| D^2 v_{h} \|_{ T }^{  }.
\end{split}
\end{equation}
Combining \eqref{eq:inv1} and \eqref{eq:inv2}, we establish that
\begin{equation}
    \label{eq:general}
\abs{ v_{h} }_{l,F}  \lesssim h^{m-l - \frac{1}{2}} \abs{ v_{h} }_{m, T}
\text{ for } l \le m.
\end{equation}

\subsection{Cea's lemma}%
\label{sub:ceas_lemma}

Assume that we have a discrete bilinear form $a_{h}: X_{h}\times X_{h} \to \mathbb{R} $ and let $X _{h} \subseteq  V $ be the discrete conform polynomial space. We transition the problem to find a solution, $u_{h} \in  \mathcal{V}_{h}$, so it holds that $a\left( u_{h},v_{h} \right)  = l\left( v_{h} \right) \ \  \forall v_{h} \in X _{h} $.
Since the method is conform, i.e., $X _{h} \subseteq  V $, does it exists a exact solution, $u \in  \mathcal{V}$, such that \(
a \left( u, v_{h} \right)  = l\left( v_{h} \right)  \ \  \forall v_{h} \in  X _{h}.
\)
Furthermore, the problem is said to be strongly consistent since it fulfills the Galerkin orthogonality property, that is $ a\left( u -u_{h} , v_{h} \right)  =0$. Thus, if $u_{h},v_{h} \in  X _{h}$, then
\begin{equation}
\label{eq:cealemma_proof}
    \begin{split}
\alpha \| u -u_{h} \|_{ V  }^{ 2 } & \le  a\left( u - u_{h}, u - u_{h}  \right)    \\
&= a\left( u - u_{h}, u -v_{h} \right) - a\left( u -u_{h}, v_{h} - u_{h} \right)  \\
 &  \le  M \| u - u_{h} \|_{ V  }^{  }  \| u - v_{h} \|_{ V  }^{  }
    \end{split}
.\end{equation}
Hence, we now have the so-called Ceas lemma, \[
\| u - u_{h} \|_{ V  }^{  }  \lesssim  \inf_{v_{h} \in X_{h} } \|  v_{h} - u \|_{V  }^{  }.
\]
A useful property is that for a conformal numerical method to converge can we now simply require \[
\lim_{h \to 0}  \inf_{v_{h} \in  X_{h}}  \| v - v_{h} \|_{ V  }^{  } = 0 \quad  \forall v \in V.
\]
In that case will $\| u - u_{h} \|_{ V  }^{  }  \to  0$, $h \to  0$. Hence, if this requirement is fulfilled, the numerical methods will converge to a unique solution.
For more information, see \cite[p. 66]{quartdiff}.

In combination with Corollary \ref{cor:celement_apriori}, is Cea's lemma very handy to construct a priori estimates. However, Ceas lemma as it stands does assume conform methods $X_{h} \subset X$, hence, we must be cautious for broken Sobolev spaces.




