

\section{Evolutionary dynamics of the Willmore flow}%
\label{sec:evolutionary_pde_s_of_the_willmore_flow}


The goal is to derive the evolutionary dynamics of the Willmore energy $\eqref{eq:WE} $.

Recall that we define the velocity \eqref{eq:vel}to only have a normal component, i.e., $v\left( x \right)  = V \nu $.
The shape derivative for \eqref{eq:WE} in the direction of some velocity $v \in \left[ H^{1}\left( \Gamma  \right)  \right]^3   $ has the form \[
d\mathcal{E} \left( \Gamma; v  \right)  = \int_{\Gamma }^{} \left( - \Delta _{\Gamma } H + \frac{1}{2} H^{3} - H \left\lvert A \right\rvert^2  \right) V
\]
A complete derivation of the shape derivative can be found in \cite[Corally 4.7]{dougan2012first}. Consequently, by applying the gradient flow in \eqref{eq:gradient_flow} and using that $\| v \|_{ \Gamma  }^{  }  = \| V \|_{ \Gamma   }^{2  }   $ can
we easily see that,
\[
      \| V \|_{ \Gamma   }^{2  } = \int_{\Gamma }^{} V^2 = -d \mathcal{E} \left( \Gamma ;v \right).
\]
Hence, the gradient flow is equivalent to

\begin{equation}
\label{eq:gradient_velocity}
V  =   \Delta _{\Gamma } H + Q,
\end{equation}
\[
\]
where we denote the nonlinear term as $Q  = - \frac{1}{2} H^{3} + H \left\lvert A \right\rvert^2$.
\todo[inline]{ Need to define a way to compute $\Delta _{\Gamma } H $ in the background theory. }

From \cite[Lemma 2.1]{kovacs2021convergent} it derived that \eqref{eq:gradient_velocity} must satisfy the following material derivatives,
\[
    \begin{split}
\frac{D}{Dt}H & = - \left( \Delta _{\Gamma } + \left\lvert A \right\rvert ^2   \right) V, \\
\frac{D}{Dt} \nu & = \left( -\Delta _{\Gamma } + \left( HA - A^2 \right)  \right) z  \\
&  + \left\lvert \nabla _{\Gamma } H \right\rvert ^2   \nu - 2\left( \nabla _{\Gamma }\cdot \left( A \nabla _{\Gamma } H \right)  \right) \nu  \\
  & -A^2 \nabla _{\Gamma } H  - \nabla _{\Gamma } Q.
    \end{split}
\]
Here is the substitution variable introduced s.t. $z = \Delta  _{\Gamma } \nu  + \left\lvert A \right\rvert ^2 \nu $.

It exists methods which do not exploit the material derivatives \cite{bonito2010parametric, bartezzaghi2016isogeometric}.However, it turns out that including these material derivatives brings additional computational costs, but provides so-called full-order
approximation to the mean curvature, $H$, and the normal vector, $\nu $, and ,thus, allows us to construct rigorous convergence proofs for evolving surface FEM, see \cite{kovacs2021convergent, binz2022convergent}.
\todo[inline]{ Should probably find sources with Reynolds theorem or something for why material derivatives is used. }

Recent work has proposed that current method may not conserve the mesh quality while the surface is restricted to evolve along the normal velocity. Thus, a new variation of the standard methods has been considered by introducing an tangential
velocity component via the equation  $H = - v\cdot \nu  $. Hence, also allowing the mesh to be less deformed, see more at \cite{hu2022evolving}. However, in this report will we not consider it.

Finally, we end up with the following strong form of the second-order evolutionary system of PDE.
\begin{subequations}
    \label{eq:WE_strong_form}
    \begin{align}
\frac{d}{dt}H & = -  \Delta _{\Gamma }V - \left\lvert A \right\rvert ^2 V    , \\
V  & =   \Delta _{\Gamma } H + Q, \\
\frac{d}{dt} \nu & = \left( -\Delta _{\Gamma } + \left( HA - A^2 \right)  \right) z \nonumber \\
& \quad   + \left\lvert \nabla _{\Gamma } H \right\rvert ^2   \nu \nonumber  \\
 & \quad - 2\left( \nabla _{\Gamma }\cdot \left( A \nabla _{\Gamma } H \right)  \right) \nu \nonumber  \\
  & \quad  -A^2 \nabla _{\Gamma } H  - \nabla _{\Gamma } Q, \\
z & = \Delta  _{\Gamma } \nu  + \left\lvert A \right\rvert ^2 \nu \\
    \end{align}
\end{subequations}
where the terms are,
\[
    \begin{split}
\frac{d}{dt} x  &= v,\\
v & = V\nu, \\
Q & =  - \frac{1}{2} H^{3} + H \left\lvert A \right\rvert^2, \\
A & = \nabla _{\Gamma } \nu
    \end{split}
\]
Recall that the material derivative operator $\frac{D}{Dt} $ is simply equivalent to the time derivative $\frac{d}{dt}$, thus, it is now possible to apply normal techniques for time discretization.

\section{Weak formulation of Willmore flow}%
\label{sub:weak_formulation}

The FEM is based on approximating a PDE using the weak form.
From \cite{kovacs2021convergent} has it been shown that the weak form for the dynamics presented in \eqref{eq:WE_strong_form} can we written in the following weak form. We

Let us denote the following trial and test functions,
We want to find the following trial functions,
\[
    \begin{split}
& ( H \times V \times \nu  \times z ) \in \\
&\left( H^{1}\left( \Gamma  \right), H^1 \left( \Gamma  \right), \left[ H^{1} \left( \Gamma  \right)  \right] ^3, \left[ H^{1}\left( \Gamma  \right)  \right]^3   \right),
    \end{split}
\]
s.t. for all test functions,
\[
    \begin{split}
& ( \chi_{H}  \times \chi _{V} \times \chi _{\nu }  \times \chi _{z} ) \in \\
 &\left( H^{1}\left( \Gamma  \right), H^1 \left( \Gamma  \right), \left[ H^{1} \left( \Gamma  \right)  \right] ^3, \left[ H^{1}\left( \Gamma  \right)  \right]^3   \right),
    \end{split}
\]
the following system of weak system of PDE's is satisfied.

\begin{subequations}
\begin{align}
\label{eq:WE_weak_form}
\left( \frac{d}{dt}H, \chi _{H} \right)_{\Gamma } =&  \left( \nabla _{\Gamma } V, \chi _{H} \right) _{\Gamma } \nonumber \\
                                                   &- \left( \left\lvert A \right\rvert ^2 V, \chi _{H} \right) _{\Gamma }   \\
\left( V, \chi _{V} \right) =& -\left( \nabla _{\Gamma } H, \nabla _{\Gamma } \chi _{V} \right) \nonumber \\
 & + \left( Q, \chi _{V} \right)   \\
\left( \frac{d}{dt} \nu , \chi _{\nu } \right)_{\Gamma } =& \left( \nabla _{\Gamma }z, \nabla _{\Gamma } \chi _{\nu } \right) _{\Gamma }\nonumber   \\
 & + \left( ( HA - A^2  )z,\chi_\nu  \right)_{\Gamma }   \nonumber \\
& + \left( \left\lvert \nabla _{\Gamma } H \right\rvert^2 \nu + A^2\nabla _{\Gamma } H, \chi _{\nu }  \right) \nonumber  \\
 & + 2 \left( A \nabla _{\Gamma } H, \nabla _{\Gamma } \chi _{\nu } \nu  \right)\nonumber    \\
 &  + \left( Q, \nabla _{\Gamma } \chi _{\nu }  \right)_{\Gamma } \nonumber  \\
  &- \left( QH\nu , \chi _{\nu } \right) \\
\left( z, \chi _{z} \right) _{\Gamma }  =& - \left( \nabla _{\Gamma } \nu , \nabla _{\Gamma } \chi _{z} \right) \nonumber \\
 & + \left( \left\lvert A \right\rvert ^2 \nu , \chi _{z} \right)
.\end{align}
\end{subequations}













